\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

The following features will be shown in our Demo:

\begin{itemize}
    \item Logging in
    \item Object placement
    \item Object generation
    \item Go over the map
    \item Go back to the realm screen
    \item Show a tour
\end{itemize}


\section{Team Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8\\
Avanish Ahluwalia & 8\\
Russell Davidson & 8\\
Rafey Malik & 8\\
Abdul Zulfiqar & 8\\
\bottomrule
\end{tabular}
\end{table}


\section{Supervisor/Stakeholder Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 0\\
Avanish Ahluwalia & 0\\
Russell Davidson & 0\\
Rafey Malik & 0\\
Abdul Zulfiqar & 0\\
\bottomrule
\end{tabular}
\end{table}

Our team does not have any supervisor or stakeholder.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Avanish Ahluwalia & 0\\
Russell Davidson & 1\\
Rafey Malik & 1\\
Abdul Zulfiqar & 0\\
\bottomrule
\end{tabular}
\end{table}

We ensured that at least one team member attended the lecture and the others were briefed afterwards.

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Avanish Ahluwalia & 2\\
Russell Davidson & 3\\
Rafey Malik & 2\\
Abdul Zulfiqar & 3\\
\bottomrule
\end{tabular}
\end{table}

On the meeting that was missed by Avanish and Rafey, they passed on their questions for Chris to Russell and Abdul, and were then briefed about the meeting afterwards.

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 11 & 100\% \\
Avanish Ahluwalia & 1 & 9.1\%\\
Russell Davidson & 4 & 36.4\%\\
Rafey Malik & 2 & 18.2\%\\
Abdul Zulfiqar & 4 & 36.4\%\\
\bottomrule
\end{tabular}
\end{table}

Some team members make one large commit rather than multiple smaller commits, which is why the results may not be indicative of how much work they have done.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Avanish Ahluwalia & 1 & 0\\
Russell Davidson & 2 & 0\\
Rafey Malik & 6 & 0\\
Abdul Zulfiqar & 2 & 0\\
\bottomrule
\end{tabular}
\end{table}

We did not formally assign issues on github, but rather informally split the work in the comments of our team meetings issues.

\section{CICD}

We used CICD in the server to quickly re-deploy the latest versions of our system.

\end{document}